\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2021-12-16 main.tex
clean up

\textbf{Motivation}

@@

\textbf{Existing packages}

@@

\textbf{Our new data structure for spatio-temporal data} This paper
describes the implementation of a new spatio-temporal data structure:
\pkg{cubble}. \pkg{cubble} implements a relational data structure that
uses two forms to manage the switch between spatial and temporal
dimension. With this structure, users can manipulate the spatial or
temporal dimension separately, while leaves the linking of two
dimensions to \textbackslash pkg\{cubble\textbackslash pkg\{. The
software is available from the Comprehensive R Archive Network (CRAN) at
{[}CRAN link{]}. \newline

\textbf{Section division}

@@

Spatio-temporal data usually come in various forms and Figure
\ref{fig:cubble-diagram} shows four examples of this. No matter which
form the data is in, these formats share some common components that
characterise spatio-temporal data. A spatial identifier (\texttt{id} in
the diagram) is the unique identifier of each site. The temporal
identifier (\texttt{t} in the diagram) prescribes the time stamp each
site is recorded. Coordinates, comprising of latitude and longitude
(\texttt{lon} and \texttt{lat} in the diagram), locates each site on the
map. These identifiers will be the building blocks for the data
structure introduced below. Other variables in the data can be
categorised into two groups: spatial variables that are invariant at
each time stamp for every site, i.e.~the name or code of the weather
station and temporal variables that varies with time.

@@

\caption[Illustration of incoming data formats for spatio-temporal data]{Illustration of incoming data formats for spatio-temporal data. (1) Data comes in as a single table; (2) Separate tables for spatial and temporal variables; (3) A single table with all the parameters used to query the database and a separate table for queried data; and (4) Cubical data in array or NetCDF format.}\label{fig:cubble-diagram}
\end{figure}
\end{CodeChunk}

In a cubble, there are two forms: nested form and long form, and Figure
\ref{fig:def-cubble} sketches the two forms along with the associated
attributes. The decision on which form to use is output-oriented,
meaning analysts need to first think about whether the output of a
particular operation is identified only by the spatial identifier, or a
combination of spatial and temporal identifier. The nested cubble is
suitable for working with operations that are only identified by site
and this type of operation can be a pure manipulation of spatial
variables, or a summary of temporal variables by site (i.e.~the output
of counting the number of raining day is only identified by sites and
hence should be performed with the nested form). Underneath the nested
form, a cubble is built from a row-wise dataframe (\texttt{rowwise\_df})
where each site forms a separate group. This structure simplifies the
calculation that involves temporal variables by avoiding the use of
\texttt{map} syntax when working with list-column.

@@

\caption[Illustration of nested and long cubble]{Illustration of nested and long cubble.}\label{fig:def-cubble}
\end{figure}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeOutput}
# cubble:  date, id [5]: long form
# bbox:    [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# spatial: lat [dbl], long [dbl], elev [dbl], name [chr], wmo_id [dbl]
   id          date        prcp  tmax  tmin
   <chr>       <date>     <dbl> <dbl> <dbl>
 1 ASN00009021 2020-01-01     0  31.9  15.3
 2 ASN00009021 2020-01-02     0  24.9  16.4
 3 ASN00009021 2020-01-03     6  23.2  13  
 4 ASN00009021 2020-01-04     0  28.4  12.4
 5 ASN00009021 2020-01-05     0  35.3  11.6
 6 ASN00009021 2020-01-06     0  34.8  13.1
 7 ASN00009021 2020-01-07     0  32.8  15.1
 8 ASN00009021 2020-01-08     0  30.4  17.4
 9 ASN00009021 2020-01-09     0  28.7  17.3
10 ASN00009021 2020-01-10     0  32.6  15.8
# ... with 1,820 more rows
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeOutput}
# cubble:  date, id [5]: long form
# bbox:    [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# spatial: lat [dbl], long [dbl], elev [dbl], name [chr], wmo_id [dbl]
   id          date        prcp  tmax  tmin  long   lat
   <chr>       <date>     <dbl> <dbl> <dbl> <dbl> <dbl>
 1 ASN00009021 2020-01-01     0  31.9  15.3  116. -31.9
 2 ASN00009021 2020-01-02     0  24.9  16.4  116. -31.9
 3 ASN00009021 2020-01-03     6  23.2  13    116. -31.9
 4 ASN00009021 2020-01-04     0  28.4  12.4  116. -31.9
 5 ASN00009021 2020-01-05     0  35.3  11.6  116. -31.9
 6 ASN00009021 2020-01-06     0  34.8  13.1  116. -31.9
 7 ASN00009021 2020-01-07     0  32.8  15.1  116. -31.9
 8 ASN00009021 2020-01-08     0  30.4  17.4  116. -31.9
 9 ASN00009021 2020-01-09     0  28.7  17.3  116. -31.9
10 ASN00009021 2020-01-10     0  32.6  15.8  116. -31.9
# ... with 1,820 more rows
\end{CodeOutput}
\end{CodeChunk}

@@

After we have got \texttt{cluster\_nested}, spatial and temporal data at
both levels can be easily obtained. Figure \ref{fig:hierachical}
illustrate the relationship between the long and nested form cubble at
both site and cluster level. More description on this. Start with the
original \texttt{station\_nested}, \texttt{stretch()} expands the
\texttt{ts} column with each station (\texttt{id}) forming a group and
attach variables invariant to \texttt{id} as an attribute.
\texttt{switch\_key()} changes the \texttt{key} from \texttt{id} to
\texttt{cluster} and nests all the spatial variables that variant to
\texttt{cluster}. \texttt{stretch()} \texttt{cluster\_nested} will store
variables that are invariant to \texttt{cluster} as a tibble in the
attribute.

@@

@@

@@

The cubble structure fits in naturally with the interactive graphic
pipeline discussed in the literature
\citep{buja1988elements, buja1996interactive, sutherland2000orca, xie2014reactive, cheng2016enabling}.
Diagram \ref{fig:interactive-workflow} illustrates how linking works
with the two forms in a cubble, where a time series plot is created with
the long cubble and a map is created with the nested cubble. When a user
action is captured from the map, the site will be activated in the
nested cubble. Then, the nested cubble will communicate to the long
cubble to activate all the observations with the same \texttt{id}. The
long cubble will then highlight the activated series in the time series
plot.

The linking is also available from the time series plot to the map. The
selection on the time series is through selecting the point on the time
series and once a point is selected, it will be activated in the long
cubble. All the observations that share the same \texttt{id}, either in
the long and nested cubble, are then activated. This includes other
points in the same time series in the long cubble and the corresponding
observation of site in the nested cubble. These activated observations
will then being reflected in the updated plots and Diagram
\ref{fig:interactive-workflow-2} in the Appendix illustrates this
process.

@@

{\centering \includegraphics[width=1\linewidth,height=0.4\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/diagram-keynotes/diagram-keynotes.003}

@@

\caption[demon interactivity]{demon interactivity}\label{fig:interactive-workflow}
\end{figure}
\end{CodeChunk}

@@

Bureau of Meteorology (BoM) collects climate variables. This variables
can be openly queried via \texttt{rnoaa}. \texttt{weatherdata} provides
a readily available copy of several
data.\texttt{weatherdata::historical\_tmax} provides historical maximum
temperature recorded for Australian stations with the earliest dating
back to 1859 and this can be used to understand the change of maximum
temperature from a past period to nowadays. Figure
\ref{fig:glyphmap-workflow} shows the steps involved from the initial
data to the final glyph map in Figure \ref{fig:glyphmap}.

@@

@@

\caption[demon code]{demon code}\label{fig:glyphmap-workflow}
\end{figure}
\end{CodeChunk}

{\centering \includegraphics[width=1\linewidth,height=0.7\textheight]{figures/basic-manipulation}

\caption[asdfasd]{asdfasd}\label{fig:glyphmap}
\end{figure}
\end{CodeChunk}

@@

{\centering \includegraphics[width=1\linewidth,height=0.9\textheight]{figures/aggregation}

@@

\caption[sdfasdf]{sdfasdf}\label{fig:aggregation}
\end{figure}
\end{CodeChunk}

@@

\begin{CodeChunk}

\begin{center}\includegraphics{figures/unnamed-chunk-7-1} \end{center}

\end{CodeChunk}

{\centering \includegraphics{figures/unnamed-chunk-8-1}

\caption[shtishisaasdf]{shtishisaasdf}\label{fig:unnamed-chunk-8}
\end{figure}
\end{CodeChunk}

Now we use \texttt{match\_sites()} to first pair the weather stations
with the river gauges spatially and then apply the temporal matching on
\texttt{prcp}. We will construct the interval based on peaks in
\texttt{climate} since we would expect a lag effect for precipitation to
flow into the river and cause a raise in river level, hence
\texttt{temporal\_independent\ =\ climate}. We select the 30 highest
peak from the series to construct the match by setting
\texttt{temporal\_n\_highest\ =\ 30}. This is a tuning parameter and you
can start with 10\% of the points of one series (here we have daily data
for a year, 10\% is roughly 30 points). \texttt{temporal\_min\_match}
filters out pairs don't have enough match and to return all the pairs,
set \texttt{temporal\_min\_match} to \texttt{0}.

\begin{CodeChunk}
\begin{CodeOutput}
# cubble:   id [8]: nested form
# bbox:     [144.52, -37.73, 146.06, -36.55]
# temporal: date [date], prcp [dbl]
  id          name                lat  long type  ts        .dist .group n_match
  <chr>       <chr>             <dbl> <dbl> <chr> <list>    <dbl>  <int>   <int>
1 405234      SEVEN CREEKS @ D~ -36.9  146. river <tibble ~  6.15      5      21
2 ASN00082042 strathbogie       -36.8  146. clim~ <tibble ~  6.15      5      21
3 404207      HOLLAND CREEK @ ~ -36.6  146. river <tibble ~  8.54     10      21
4 ASN00082170 benalla airport   -36.6  146. clim~ <tibble ~  8.54     10      21
5 230200      MARIBYRNONG RIVE~ -37.7  145. river <tibble ~  6.17      6      19
6 ASN00086038 essendon airport  -37.7  145. clim~ <tibble ~  6.17      6      19
7 406213      CAMPASPE RIVER @~ -37.0  145. river <tibble ~  1.84      1      18
8 ASN00088051 redesdale         -37.0  145. clim~ <tibble ~  1.84      1      18
\end{CodeOutput}
\end{CodeChunk}

@@

{\centering \includegraphics[width=1\linewidth]{figures/unnamed-chunk-11-1}

@@

\caption[..]{...}\label{fig:unnamed-chunk-11}
\end{figure}
\end{CodeChunk}

@@

\begin{CodeChunk}

\begin{center}\includegraphics[width=1\linewidth,height=0.3\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/linking} \end{center}

\end{CodeChunk}

\begin{CodeChunk}

\begin{center}\includegraphics[width=0.5\linewidth,height=0.3\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/popup} \end{center}

\end{CodeChunk}

@@

{\centering \includegraphics[width=1\linewidth,height=0.4\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/diagram-keynotes/diagram-keynotes.007}

@@

\caption[demon interactivity]{demon interactivity}\label{fig:interactive-workflow-2}
\end{figure}
\end{CodeChunk}

@@

\hypertarget{old-stuff}{%
\section{Old stuff}\label{old-stuff}}

In the temporal aspect, the \texttt{tsibble} \citep{tsibbles} structure
and its tidyverts ecosystem have provided a {[}\ldots{} {]} workflow to
work with temporal data. In a tsibble structure, temporal data is
characterised by \texttt{index} and \texttt{key} where \texttt{index} is
the temporal identifier and \texttt{key} is the identifier for multiple
series, which could be used as a spatio identifier. However, a tsibble
object, by construction, always requires the \texttt{index} in its
structure. This makes it less appealing for spatio-temporal data since
the output of calculated spatio-specific variables (i.e.~features of
each series) don't have the time dimension. Analysts will either need to
have an additional step to join this output to the original tsibble or
operate with variables stored in two separate objects. In addition, the
long form structure of a tsibble object means spatio variables
(i.e.~longitude, latitude, and features of each series if joined back to
the tsibble) of each spatio identifier will be repetitively recorded at
each timestamp. This repetition is unnecessary and would inflate the
object size for long series.

\hypertarget{create-a-cubble}{%
\section{Create a cubble}\label{create-a-cubble}}

The creation of a cubble requires the site identifier (\texttt{key}), as
well as the spatial (\texttt{coords}) and temporal (\texttt{index})
identifier. \texttt{climate\_flat} is already a tibble and it uses
\texttt{id} to identify each station, \texttt{date} as the time
identifier, and \texttt{c(long,\ lat)} as the spatial identifier. To
create a cubble for this data, use:

Most of the time, spatio-temporal data doesn't come into this form and
analysts need to query the climate variables based on station metadata.
\textcolor{red}{This is also a problem illustrated in Section 3.5 in @tidydata. Here we provide a structured way to query this data based on the row-wise operator and nested list.}
For this type of task, one can structure a metadata into a tibble and
use row-wise operator to query the climate variables into a nested list.
As an example here we demonstrate the workflow to find the 5 closest
stations to Melbourne. We first create a station data frame with the 5
target stations.

\begin{CodeChunk}
\begin{CodeOutput}
# A tibble: 5 x 8
  id            lat  long  elev name                 wmo_id  dist city     
  <chr>       <dbl> <dbl> <dbl> <chr>                 <dbl> <dbl> <chr>    
1 ASN00086038 -37.7  145.  78.4 essendon airport      95866  10.8 melbourne
2 ASN00086282 -37.7  145. 113.  melbourne airport     94866  20.1 melbourne
3 ASN00086077 -38.0  145.  12.1 moorabbin airport     94870  21.9 melbourne
4 ASN00088162 -37.4  145. 528.  wallan (kilmore gap)  94860  48.1 melbourne
5 ASN00087113 -38.0  144.  10.6 avalon airport        94854  48.8 melbourne
\end{CodeOutput}
\end{CodeChunk}

We can query the climate information into a nested list named
\texttt{ts} for each station with the \texttt{rowwise()} operator. To
create a cubble, supply the same identifiers as with the first example.

\begin{CodeChunk}
\begin{CodeOutput}
# cubble:   id [5]: nested form
# bbox:     [144.47, -38.03, 145.1, -37.38]
# temporal: date [date], prcp [dbl], tmax [dbl], tmin [dbl]
  id            lat  long  elev name                 wmo_id  dist city   ts     
  <chr>       <dbl> <dbl> <dbl> <chr>                 <dbl> <dbl> <chr>  <list> 
1 ASN00086038 -37.7  145.  78.4 essendon airport      95866  10.8 melbo~ <tibbl~
2 ASN00086282 -37.7  145. 113.  melbourne airport     94866  20.1 melbo~ <tibbl~
3 ASN00086077 -38.0  145.  12.1 moorabbin airport     94870  21.9 melbo~ <tibbl~
4 ASN00088162 -37.4  145. 528.  wallan (kilmore gap)  94860  48.1 melbo~ <tibbl~
5 ASN00087113 -38.0  144.  10.6 avalon airport        94854  48.8 melbo~ <tibbl~
\end{CodeOutput}
\end{CodeChunk}

Below are the how the nested and long form look like for Australia
climate data, which records daily precipitation, maximum and minimum
temperature for 55 stations across Australia from 2015- 2020. Notice
that each station forms a group in both forms and specifically, the
nested and long form have a underlying \texttt{rowwise\_df} and
\texttt{grouped\_df} respectively.

With a cubic framework on mind, different types of manipulation with
cubble can be thought of as slicing the cube in various way. The table
below shows how some \texttt{dplyr} verbs are mapped into the operation
in a cubble. With the existing grouping on the station, additional
grouping can be added with \texttt{group\_by} and removed with
\texttt{ungrouped}. {[}talk about why it is useful{]}

\hypertarget{cubble-operations}{%
\subsection{Cubble operations}\label{cubble-operations}}

{\centering \includegraphics[width=0.9\linewidth,height=0.5\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/diagram-keynotes/diagram-keynotes.004}

\caption[Cubble operations]{Cubble operations}\label{fig:cubble-operations}
\end{figure}
\end{CodeChunk}

>>>>

@@

@@

This paper describes the implementation of a new spatio-temporal data
structure: \pkg{cubble}. \pkg{cubble} implements a relational data
structure that uses two forms to manage the switch between spatial and
temporal dimension. With this structure, users can manipulate the
spatial or temporal dimension separately, while leaves the linking of
two dimensions to \pkg{cubble}. The software is available from the
Comprehensive R Archive Network (CRAN) at {[}CRAN link{]}. \newline

@@

Spatio-temporal data usually come in various forms and Figure
\ref{fig:illu-input} shows four examples of this. No matter which form
the data is in, these formats share some common components that
characterise spatio-temporal data. A spatial identifier (\texttt{id} in
the diagram) is the unique identifier of each site. The temporal
identifier (\texttt{t} in the diagram) prescribes the time stamp each
site is recorded. Coordinates, comprising of latitude and longitude
(\texttt{lon} and \texttt{lat} in the diagram), locates each site on the
map. These identifiers will be the building blocks for the data
structure introduced below. Other variables in the data can be
categorised into two groups: spatial variables that are invariant at
each time stamp for every site, i.e.~the name or code of the weather
station and temporal variables that varies with time.

@@

\caption[Illustration of incoming data formats for spatio-temporal data]{Illustration of incoming data formats for spatio-temporal data. (1) Data comes in as a single table; (2) Separate tables for spatial and temporal variables; (3) A single table with all the parameters used to query the database and a separate table for queried data; and (4) Cubical data in array or NetCDF format.}\label{fig:illu-input}
\end{figure}
\end{CodeChunk}

In a cubble, there are two forms: nested form and long form, and Figure
\ref{fig:illu-cubble} sketches the two forms along with the associated
attributes. The decision on which form to use is output-oriented,
meaning analysts need to first think about whether the output of a
particular operation is identified only by the spatial identifier, or a
combination of spatial and temporal identifier. The nested cubble is
suitable for working with operations that are only identified by site
and this type of operation can be a pure manipulation of spatial
variables, or a summary of temporal variables by site (i.e.~the output
of counting the number of raining day is only identified by sites and
hence should be performed with the nested form). Underneath the nested
form, a cubble is built from a row-wise dataframe (\texttt{rowwise\_df})
where each site forms a separate group. This structure simplifies the
calculation that involves temporal variables by avoiding the use of
\texttt{map} syntax when working with list-column.

@@

\caption[Illustration of nested and long cubble]{Illustration of nested and long cubble.}\label{fig:illu-cubble}
\end{figure}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeOutput}
# cubble:  date, id [5]: long form
# bbox:    [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# spatial: lat [dbl], long [dbl], elev [dbl], name [chr], wmo_id [dbl]
  id          date        prcp  tmax  tmin
  <chr>       <date>     <dbl> <dbl> <dbl>
1 ASN00009021 2020-01-01     0  31.9  15.3
2 ASN00009021 2020-01-02     0  24.9  16.4
3 ASN00009021 2020-01-03     6  23.2  13  
4 ASN00009021 2020-01-04     0  28.4  12.4
5 ASN00009021 2020-01-05     0  35.3  11.6
# ... with 1,825 more rows
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeOutput}
# cubble:  date, id [5]: long form
# bbox:    [115.97, -32.94, 133.55, -12.42]- check gap on long and lat
# spatial: lat [dbl], long [dbl], elev [dbl], name [chr], wmo_id [dbl]
  id          date        prcp  tmax  tmin  long   lat
  <chr>       <date>     <dbl> <dbl> <dbl> <dbl> <dbl>
1 ASN00009021 2020-01-01     0  31.9  15.3  116. -31.9
2 ASN00009021 2020-01-02     0  24.9  16.4  116. -31.9
3 ASN00009021 2020-01-03     6  23.2  13    116. -31.9
4 ASN00009021 2020-01-04     0  28.4  12.4  116. -31.9
5 ASN00009021 2020-01-05     0  35.3  11.6  116. -31.9
# ... with 1,825 more rows
\end{CodeOutput}
\end{CodeChunk}

@@

After we have got \texttt{cluster\_nested}, spatial and temporal data at
both levels can be easily obtained. Figure \ref{fig:illu-hier}
illustrate the relationship between the long and nested form cubble at
both site and cluster level. More description on this. Start with the
original \texttt{station\_nested}, \texttt{stretch()} expands the
\texttt{ts} column with each station (\texttt{id}) forming a group and
attach variables invariant to \texttt{id} as an attribute.
\texttt{switch\_key()} changes the \texttt{key} from \texttt{id} to
\texttt{cluster} and nests all the spatial variables that variant to
\texttt{cluster}. \texttt{stretch()} \texttt{cluster\_nested} will store
variables that are invariant to \texttt{cluster} as a tibble in the
attribute.

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/research/paper-cubble/figures/diagram-keynotes/diagram-keynotes.003}

\caption[Hierarchical structure]{Hierarchical structure}\label{fig:illu-hier}
\end{figure}
\end{CodeChunk}

@@

Figure \ref{fig:illu-matching}

{\centering \includegraphics[width=1\linewidth,height=0.3\textheight]{figures/illu-matching}

\caption[sdfasdf]{sdfasdf}\label{fig:illu-matching}
\end{figure}
\end{CodeChunk}

@@

The cubble structure fits in naturally with the interactive graphic
pipeline discussed in the literature
\citep{buja1988elements, buja1996interactive, sutherland2000orca, xie2014reactive, cheng2016enabling}.
Diagram \ref{fig:illu-interactive} illustrates how linking works with
the two forms in a cubble, where a time series plot is created with the
long cubble and a map is created with the nested cubble. When a user
action is captured from the map, the site will be activated in the
nested cubble. Then, the nested cubble will communicate to the long
cubble to activate all the observations with the same \texttt{id}. The
long cubble will then highlight the activated series in the time series
plot.

The linking is also available from the time series plot to the map. The
selection on the time series is through selecting the point on the time
series and once a point is selected, it will be activated in the long
cubble. All the observations that share the same \texttt{id}, either in
the long and nested cubble, are then activated. This includes other
points in the same time series in the long cubble and the corresponding
observation of site in the nested cubble. These activated observations
will then being reflected in the updated plots and Diagram
\ref{fig:illu-interactive-2} in the Appendix illustrates this process.

@@

@@

\caption[demon interactivity]{demon interactivity}\label{fig:illu-interactive}
\end{figure}
\end{CodeChunk}

@@

Bureau of Meteorology (BoM) collects climate variables. This variables
can be openly queried via \texttt{rnoaa}. \texttt{weatherdata} provides
a readily available copy of several data.
\texttt{weatherdata::historical\_tmax} provides historical maximum
temperature recorded for Australian stations with the earliest dating
back to 1859 and this can be used to understand the change of maximum
temperature from a past period to nowadays.

Figure \ref{fig:basic-manip}.

\begin{CodeChunk}
\begin{CodeInput}
R> tmax <- weatherdata::historical_tmax %>%
+   # filter out VIC and NSW stations
+   filter(between(stringr::str_sub(id, 7, 8), 46, 90)) %>% 
+   
+   # filter out observations in between 1971-1975 and 2016 - 2020
+   stretch() %>%
+   filter(lubridate::year(date) %in% c(1971:1975, 2016:2020)) %>%
+   mutate(month = lubridate::month(date), 
+          group = as.factor(ifelse(lubridate::year(date) > 2015, 
+                                   "2016 ~ 2020", "1971 ~ 1975"))) %>%
+   group_by(month, group) %>%
+   # summarise tmax into monthly mean for both periods
+   summarise(tmax = mean(tmax, na.rm = TRUE)) %>% 
+   
+   # filter out stations that have complete records in both periods 
+   tamp() %>%
+   filter(nrow(ts) == 24) %>% 
+   
+   # migrate longitude and latitude to the long form for making the glyph map
+   stretch() %>%
+   migrate(latitude, longitude)
R> 
R> gly <- glyphs(tmax, "longitude", "month", "latitude", "tmax",
+               height = 0.6, width = 1)
R> 
R> nsw_vic <- ozmaps::abs_ste %>% filter(NAME %in% c("Victoria", "New South Wales"))
R> 
R> ggplot() + 
+   geom_sf(data = nsw_vic, fill = "transparent") + 
+   geom_path(data = gly, 
+             aes(gx, gy, group = interaction(id, group), color = group)) +
+   scale_color_brewer(palette = "Dark2") + 
+   theme_bw() + 
+   coord_sf(xlim = c(140, 155)) + 
+   theme(legend.position = "bottom")
\end{CodeInput}
\end{CodeChunk}

@@

{\centering \includegraphics[width=1\linewidth,height=0.7\textheight]{figures/basic-manip}

@@

\caption[asdfasd]{asdfasd}\label{fig:basic-manip}
\end{figure}
\end{CodeChunk}

@@

{\centering \includegraphics[width=1\linewidth,height=0.9\textheight]{figures/basic-agg}

@@

\caption[sdfasdf]{sdfasdf}\label{fig:basic-agg}
\end{figure}
\end{CodeChunk}

@@

Now we use \texttt{match\_sites()} to first pair the weather stations
with the river gauges spatially and then apply the temporal matching on
\texttt{prcp}. We will construct the interval based on peaks in
\texttt{climate} since we would expect a lag effect for precipitation to
flow into the river and cause a raise in river level, hence
\texttt{temporal\_independent\ =\ climate}. We select the 30 highest
peak from the series to construct the match by setting
\texttt{temporal\_n\_highest\ =\ 30}. This is a tuning parameter and you
can start with 10\% of the points of one series (here we have daily data
for a year, 10\% is roughly 30 points). \texttt{temporal\_min\_match}
filters out pairs don't have enough match and to return all the pairs,
set \texttt{temporal\_min\_match} to \texttt{0}.``

@@

{\centering \includegraphics[width=1\linewidth,height=0.3\textheight]{figures/matching}

@@

\caption[asdfasd]{asdfasd}\label{fig:matching}
\end{figure}
\end{CodeChunk}

@@

Figure \ref{fig:interactive-linking} Figure \ref{fig:interactive-popup}

{\centering \includegraphics[width=1\linewidth,height=0.3\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/linking}

\caption[sdfasd]{sdfasd}\label{fig:interactive-linking}
\end{figure}
\end{CodeChunk}

{\centering \includegraphics[width=0.5\linewidth,height=0.3\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/popup}

\caption[sdfasd]{sdfasd}\label{fig:interactive-popup}
\end{figure}
\end{CodeChunk}

@@

{\centering \includegraphics[width=1\linewidth,height=0.4\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/diagram-keynotes/diagram-keynotes.005}

@@

\caption[demon interactivity]{demon interactivity}\label{fig:illu-interactive-2}
\end{figure}
\end{CodeChunk}

@@
